Static Analysis by Path Focusing

### 2011-05-09 report/report.tex
minor changes in the report

The least fixpoint of a function $\Phi^\#$ is noted $\overline{x}$ and is equal
to $\displaystyle \lim_{i \geq 0}\ x_i$, where $x_0 = \perp$ (the least element
of $A$) and $x_{i+1} = \Phi^\# (x_i)$. Instead of computing this least fixpoint,
one compute an upper approximation of it, by computing the following ascending
sequence:

@@

	Let $(P,E)$ be the control flow graph of the program.
	First, one choose a set of points $P_W \subseteq P$, so that the graph
	obtained after removing these points has no cycle. The widening operator
	will be applied at these points. The choice of $P_W$ can be guided by
	\cite{Bou92}.
	Then, one choose another set $P_R \subseteq P$ of nodes, satisfying the
	following properties:
	\begin{itemize}
	\item $I_p = \emptyset$ for each $p \in P \setminus P_R$, meaning that the initial
	points of the program are included in $P_R$.
	\item $P_W \subseteq P_R$: all the widening points are in $P_R$.
	\end{itemize}

>>>>

The least fixpoint of a function $\Phi^\#$ is noted $\overline{x}$.
Instead of computing this least fixpoint,
one compute an upper approximation of it, by computing the following ascending
sequence:

@@

	Let $(P,E)$ be the control flow graph of the program.
	First, one chooses a set of widening points $P_W \subseteq P$, so that the graph
	obtained after removing these points has no cycle. The widening operator
	will be applied at these points. The choice of $P_W$ can be guided by
	\cite{Bou92}.
	Then, one chooses another set $P_R \subseteq P$ of nodes, satisfying the
	following properties:
	\begin{itemize}
	\item $I_p = \emptyset$ for each $p \in P \setminus P_R$, meaning that the initial
	points of the program are included in $P_R$.
	\item $P_W \subseteq P_R$: all the widening points are in $P_R$.
	\end{itemize}
